---
title: My dynamic report
output: html_fragment
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo=FALSE, message=FALSE, warning=FALSE, error=FALSE)
# Load necessary package
library(tidyverse)

# Read CSV data from the URL
url <- "https://docs.google.com/spreadsheets/d/e/2PACX-1vSZy6LqnU-obLwdq3KecjVG_PIEAJ7MugO75NuYfUjxkzDA1_IHklFLTzSStqTgKNCQb5VwA0OY6T_8/pub?output=csv"
logged_data <- read_csv(url)

# View the first few rows of the data
head(logged_data)
```

```{css}
body {
  background-color: #f4f4f4;  
  font-family: Arial, sans-serif;  
  line-height: 1.6;  
  color: #333;  
  margin: 0;  
  padding: 20px;
```

## Summary Statistics

I calculate two important summary statistics: the maximum and mean of hours spent on the cell phone.

```{r}
# Rename the data for clarity
latest_data <- rename(logged_data)

# Calculate the maximum value of the hours spent on the cell phone
maximum_value_of_hours=max(latest_data$`Please estimate the approximate number of hours you were on your cell phone on the last day you filled out the questionnaire?  (Include any scenarios in which you used your cell phone, such as using it to navigate, send messages, play cell phone games, etc.)
Please fill in only one integer number for the number of hours`)
# Calculate the mean value of the hours spent on the cell phone
mean_value_of_hours=mean(latest_data$`Please estimate the approximate number of hours you were on your cell phone on the last day you filled out the questionnaire?  (Include any scenarios in which you used your cell phone, such as using it to navigate, send messages, play cell phone games, etc.)
Please fill in only one integer number for the number of hours`)

```

The *maximum number* of hours spent on the cell phone is `r maximum_value_of_hours`, and the *mean number* of hours is `r mean_value_of_hours` This shows us the range and average cell phone usage among respondents.

## Data Visualizations

# 1. Distribution of Hours Spent on Cell Phone
We will create a bar chart to show the distribution of the number of hours spent on the cell phone.

```{r}
# Create a bar plot showing the distribution of hours spent on the cell phone
ggplot(data = latest_data) + 
  geom_bar(aes(latest_data$`Please estimate the approximate number of hours you were on your cell phone on the last day you filled out the questionnaire?  (Include any scenarios in which you used your cell phone, such as using it to navigate, send messages, play cell phone games, etc.)
Please fill in only one integer number for the number of hours`)) +
  labs(x = 'Number of Hours', # X-axis label for hours
       y = 'Count',           # Y-axis label for count of responses
       title = 'Distribution of Hours Spent on Cell Phone on the Last Day') +  # Title of the chart
  theme_minimal()  # Use a minimal theme for better readability
```

# 2. Do You Think You Used Your Cell Phone for Too Long?
Next, we will create a bar chart for the responses to the question of whether respondents think they used their cell phone for too long yesterday.

```{r}
# Create a bar plot for Question 3 about whether respondents think they used their cell phone too long
ggplot(data = latest_data) + 
  geom_bar(aes(latest_data$`Do you think you used your cell phone for too long yesterday?`)) + 
  labs(x = 'Response',  # X-axis label for yes/no responses
       y = 'Count',     # Y-axis label for count of responses
       title = 'Do You Think You Used Your Cell Phone for Too Long Yesterday?') +  # Title of the chart
  theme_minimal()  # Use a minimal theme for better readability

```
